### 2014-08-13 Neutral_simul.Rmd
Add time to pvalues table

```{r simul_pomac467_T100, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

@@

# Which are not different
pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")

@@

rm(mks,psa,den2,den3)

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
pander(mks1,split.tables=Inf,caption="SRS not different")

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different")

@@

setwd(oldcd)
rm(c1,c2,Dq2,Dq1)
rm(den1,den,mks1,mks,mks100)
save.image()

@@

```{r simul_pomac467_T500, eval=T,echo=F,message=F,warning=F }

@@

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T=1000")

Dq1 <- readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt"))

mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=1000")

@@

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T500")

>>>>

```{r simul_pomac467_T100, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

@@

# Which are not different
#pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")

@@

rm(mks,psa,den2)

@@

#mks1 <- m$mPval
#mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
#pander(mks1,split.tables=Inf,caption="SRS not different")

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
#pander(mks1,caption="DqSAD not different")

@@

setwd(oldcd)
rm(Dq1,den1)
rm(den1,den,mks1,mks,mks100)
save.image()

@@

```{r simul_pomac467_T500, eval=T,echo=F,message=F,warning=F }
load(".RData")

@@

m <- compMethods_Time(bName,500,spMeta)

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T=500")

Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))

mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=500")

@@

setwd(oldcd)
rm(Dq1,m,mks1)
save.image()

@@

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T1000")
